---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# protofacs

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of protofacs is to provide tools for storing and manipulating data from
the Facial Action Coding System (FACS) 2002 edition.

## Installation

You can install the development version of protofacs from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jmgirard/protofacs")
```

## Example
```{r}
library("protofacs")
```

### Step 1: Define your coding scheme
```{r}
# Which behaviors were coded for occurrence, intensity, and asymmetry?
my_scheme <- scheme(
  list(
    occurrence = c(1, 2, 4, 6, 9, 10, 12, 14, 20, 25),
    intensity  = c(6, 12),
    asymmetry  = c(2, 6, 10, 12, 14, 20)
  )
)
my_scheme
```

### Step 2: Convert your coding from character
```{r}
# Clean up messy codes and set class
messy_codes <- c(" 12B+ 1 +L2", "T20 + 25")
clean_codes <- coding(messy_codes)
clean_codes
```

### Step 3: Generate coding matrixes
```{r}
# Generate occurrence matrix
occurrence(clean_codes, my_scheme)

# Generate intensity matrix
intensity(clean_codes, my_scheme)

# Generate asymmetry matrix
asymmetry(clean_codes, my_scheme)
```

### Step 4: Compute occurrence agreement
```{r}
compare_occurrence(coding("1+4+9"), coding("1+4+10"))
```
